%---------------------------------
% Little Children, Keep Yourselves
% From Idols
%
% Author: R Nate Crummett
%---------------------------------
\documentclass[12pt]{article}
\input{../bible}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}

\begin{document}
	\textbf{Assembly of the First Born \hfill Notes}

	Forsaking Idolatry \hfill \today
	
	\begin{quote}
		\BibleFirstJohnFiveTwentyOne{}
	\end{quote}

	\begin{quote}
		\BibleFirstJohnFiveOne{}
		\BibleFirstJohnFiveTwo{}
		\BibleFirstJohnFiveThree{}
		\BibleFirstJohnFiveFour{}
	\end{quote}

	\begin{quote}
		\BibleJohnSixteenThirtyTwo{}
	\end{quote}

	The Father has to be your peace. Not anything or anyone else.
	You slot women too high in your life. This goes back to having
	idols in your heart. Being a man means not compromising what
	you stand for for anyone, under any circumstance. Leaders cannot
	compromise.

	\begin{quote}
		\BibleJohnSixteenThirtyThree{}
	\end{quote}

	Overcome: To prevail, To conquer. Who's name does this name
	remind you of? Jacob's name Israel is one. 

	\begin{quote}
		\BibleGenesisThirtyTwoTwentyEight{}
	\end{quote}

	Overcoming the world is having power with God.

	\begin{quote}
		\BibleGenesisThirtyEight{}
	\end{quote}

	What does wrestling mean? A struggle. To overcome, you have
	to have a struggle.

	\begin{quote}
		\BibleActsFourteenTwentyTwo{}
	\end{quote}

	\begin{quote}
		\BibleMatthewTwentySixFortyOne{}
	\end{quote}

	What does it mean to overcome the world? How do you do
	it? By faith. Not through the law. What do you receive for
	overcoming the world? It doesn't matter if you keep the 
	law or not, because people without faith keep the law and 
	\textbf{sin}.

	What do you see in Genesis One? God created man by a word. 
	In Genesis Two you see what he made the man from, and how
	he does it.

	What does equal mean? Equality means equality in status, 
	quantity, degree, value.

	\begin{quote}
		\BibleGenesisFiveOne{}
	\end{quote}

	Generations: descendants.

	\begin{quote}
		\BibleGenesisTwoOne{}
	\end{quote}

	The heavens and Earth were complete.

	\begin{quote}
		\BibleGenesisOneFour{}
		\BibleGenesisOneFive{}
		\BibleGenesisOneSix{}
	\end{quote}

	You must be laser focused. Be laser focused on what other people
	say. When you really listen to them, you can catch when they make
	a slip or make a fallacy. \textbf{Listen} to other people, and you
	will ascertain very quickly whether or not people took the time
	to read and study diligently.

	\begin{quote}
		\BibleGenesisOneSeven{}
		\BibleGenesisOneEight{}
		\BibleGenesisOneNine{}
		\BibleGenesisOneTen{}
	\end{quote}

	Thus the Garden was finished.

	\begin{quote}
		\BibleGenesisTwoTwo{}
		\BibleGenesisTwoThree{}
		\BibleGenesisTwoFour{}
	\end{quote}

	Same generations. These are the generations of heaven and Earth.
	Why would God start doing the same work that he already rested
	from?

	\begin{quote}
		\BibleGenesisOneTwentySeven{}
	\end{quote}

	God knew he was going to pull the woman out of the man.

	\begin{quote}
		\BibleRevelationTwoSeven{}
	\end{quote}

	\begin{quote}
		\BibleRomansSevenTwenty{}
		\BibleRomansSevenTwentyOne{}
		\BibleRomansSevenTwentyTwo{}
		\BibleRomansSevenTwentyThree{}
		\BibleRomansSevenTwentyFour{}
	\end{quote}

	Adam could not deliver Eve. Moses could not deliver his people.
	God has to be the one to do this. The deliverance from death
	comes from God.

	Any man who gives power and authority is a God. The law
	tells us this. Our God wants us to be Gods. Our God wants
	us to be like him. Only in throne and in power he will be
	greater than us. God gave Adam dominion. God gave him authority
	to name everything, and everything was submitted to him.
	Adam was a God.

	Adam did not prevail, therefore he did not have a right to
	the tree of life.

	Adam did not sin when he told God the truth about what the
	woman did. Do not read emotionally into the text. Adam answered
	the question. Did the woman throw the serpent under the bus?
	She told God what happened. Understand the message: take
	accountability for your desires, make sure your desire is
	towards the word. Keep my desire to my God, and you will never
	transgress the word. This is simple to execute, not complicated.
	
	If you take pleasure in what he takes delight in, you will
	never go wrong. Justice, loving kindness, mercy. Replace your
	desire with his. The lesson to learn is to not desire things
	contrary to the will of God.

	Do not blame a woman. Especially if you are a man. Do not
	blame another person. Do not let the fault of another make
	you miss the lesson \textbf{God is trying to teach you}.

	Everybody is not you. Everybody doesn't have your people, for
	better or worse. Not everyone knows what it is like to be loved.
	Not everyone knows what is is to have someone sacrifice for them.
	Not everyone has experienced that. Some people come from very
	adverse circumstances. Some were not loved. What do you think that
	does to a person? It is destructive to not receive love from
	your mother. It makes a person not care about life. Do you
	understand why these boys are out here killing each other? How
	would someone be a functional adult coming from this? \textbf{
	Listen to people and it is obvious they are missing something.}
	When you do not know what to look for though, you will miss it.
	Also know when you are not skilled enough to address and issue,
	and help them by leading them to someone who can help. Your focus
	needs to be on making other people whole.

	\begin{quote}
		\BibleRomansFifteenOne{}
	\end{quote}

	No ones above highs and lows of life. Life 
	hurts. Everyone is subject to like passions. Eliyahu begged
	for death; but would you tell him he is wrong? Remember
	people are human and this world is tough.

	Mental and emotional lowness can happen even with the spirit. 
	The pastor is not invincible. The preacher is human. The Lord
	himself was sorrowful even unto death. God had to send an angel
	from heaven to strengthen him in the final hours.

	If you do not think you need to do anything for the men that
	labor on your behalf, you are wicked.

	\begin{quote}
		\BibleHebrewsThirteenTen{}
		\BibleHebrewsThirteenEleven{}
		\BibleHebrewsThirteenTwelve{}
		\BibleHebrewsThirteenThirteen{}
		\BibleHebrewsThirteenFourteen{}
		\BibleHebrewsThirteenFifteen{}
		\BibleHebrewsThirteenSixteen{}
		\BibleHebrewsThirteenSeventeen{}
	\end{quote}
	
	You are going to have emotions. You are always going to deal
	with the flesh. The self control in you prevents you from
	sinning against God. Temperance, or having control of yourself,
	is not popular.

	\begin{quote}
		\BibleRevelationTwoEleven{}
	\end{quote}

	If you prevail, the second death will not touch you.

	\begin{quote}
		\BibleRevelationTwoSeventeen{}
	\end{quote}

	\begin{quote}
		\BibleRevelationTwoTwentySeven{}
		\BibleRevelationTwoTwentyEight{}
	\end{quote}

	If you overcome, you will be given power. And he will also
	give you Lucifer.
	To beat idols, you will need to wrestle with them. Our faith
	is the victory over the world.

	\begin{quote}
		\BibleFirstJohnFiveFour{}
	\end{quote}

	Faith is the righteousness of God. Abraham believed, and it
	was counted to him as righteousness. What does faith mean
	from Gods perspective? Steadfast, faithful. God is faithful.
	His word will come to pass. This is our hope.

	\begin{quote}
		\BibleDeuteronomyThirtyTwoTwenty{}
	\end{quote}

	A kinsman redeemer must be a man. And Hosea told us he would send
	us a redeemer.

	\begin{quote}
		\BibleHoseaThirteenFourteen{}
	\end{quote}

	To act as a kinsman redeemer is what he will do to ransom us
	back from Sheol. The kinsman redeemer bought us back from
	death. Who is the ga'al? You must identify him!

	\begin{quote}
		\BibleHoseaTwelveThree{}
		\BibleHoseaTwelveFour{}
	\end{quote}

	Prevailed: the ability to have victory, to win. You need to win
	with God. David beat Goliath with God, with faith. When Jericho's
	walls fell, it was by faith in God. Do not fall for the trap that
	it was by Davids strength he prevailed.

	Out of the abundance of the heart the mouth speaks. Once somebody
	shows you who they are \textbf{you need to believe them}. If
	someone shows you they do not believe, you need to believe them.

	\begin{quote}
		\BibleGenesisThreeOne{}
		\BibleGenesisThreeTwo{}
		\BibleGenesisThreeThree{}
		\BibleGenesisThreeFour{}
	\end{quote}

	\begin{quote}
		\BibleGenesisTwoSeven{}
	\end{quote}

	Surely die: death death. Emphasis. When the woman transgressed,
	they received a punishment. David pronounced death on his own
	head when he sinned. But God put his sin away, and God punished
	him. David did die eventually. God did not kill him in the day
	of his sin though.

	In Adam we all die. God pushes the sin off to the third and fourth
	generation. God does not clear the sinner. He forgives the sinner,
	and then consequences come. The curses came so that they would 
	learn obedience through suffering.

	Do not ever speak on someone more righteous than yourself.

	\begin{quote}
		\BibleSongOfSolomonEightOne{}
		\BibleSongOfSolomonEightTwo{}
		\BibleSongOfSolomonEightThree{}
		\BibleSongOfSolomonEightFour{}
		\BibleSongOfSolomonEightFive{}
		\BibleSongOfSolomonEightSix{}
	\end{quote}

	\begin{quote}
		\BiblePsalmTwoTwelve{}
	\end{quote}

	Jerusalem is the mother of us all. What is the spiced wine?
	Take; eat; this is my blood, shed for the remission of sins.

	If you are not willing to die for the woman you are with, do
	not marry her. You should be willing to lay down your life for
	her, like the Lord did for his church.

	\begin{quote}
		\BibleSongOfSolomonEightSeven{}
	\end{quote}

	Can't anything quench the love of God. It is unquenchable.

	Contemned: to despise, hold as invaulable. There has to be
	a love present to die for another person. Most people do
	not love anyone enough to die, so it is tough to understand
	what the Lord's love is like. It is tough to serve like him.

	By faith we have access to the hope of God.

	\begin{quote}
		\BibleRomansFiveFive{}
	\end{quote}

\end{document}
